Sociology of Education Association Proposal

### 2020-10-30 sea_conference/soc_of_ed_proposal.Rmd
gotta go!

This paper analyzes off-campus recruiting visits to U.S. private high schools made by a sample of public research universities and sample of selective private colleges and universities in 2017.

We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions. Analyses are informed by two broad, related questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?

@@

>>>>

This paper uses social network methods to analyze off-campus recruiting visits to U.S. private high schools, utilizing data we collected in 2017 from a sample of public research universities and a sample of selective private colleges and universities.  Analyses are broadly informed by two, related questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)? Third, after examining visit patterns separately for public and private postsecondary institutions, we examine similarities and differences across public versus private postsecondary institutions.

This study builds from previous research analyzing recruiting visits by public research universities. As described in more detail below, 12 of the 15 public research universities in our sample made far more out-of-state visits than in-state visits, a finding antithetical to the stated mission of most public research universities. These out-of-state visits focused on wealthy, predominantly white schools and communities. Additionally, most public research universities made a disproportionate number of out-of-state visits to private schools, but visited few in-state private schools. [TRIM]

# DATA/METHODS

@@

PREVIOUS TEXT
We will focus on network analyses of visits by colleges and universities to private high schools. Analyses are motivated by two, related research questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
